\hypertarget{course-schedule}{%
\section{Course Schedule}\label{course-schedule}}

\textbf{Subject to Change}. All changes will be announced in-class,
through email, and on the \href{https://lms.cofc.edu}{OAKS} course page.
All the readings for the course will be available on
\href{https://lms.cofc.edu}{OAKS}.

\hypertarget{readings}{%
\subsection{Readings}\label{readings}}

\begin{itemize}
\item
  \faBook \hspace{0.005in} \textbf{RP}: Rinfret, Sara R., and Michelle
  C. Pautz. 2019. \emph{US Environmental Policy in Action}. 2nd ed.~New
  York, NY: Palgrave Macmillan.

  \begin{itemize}
  
  \item
    Chapters posted on \href{https://lms.cofc.edu}{OAKS}
  \end{itemize}
\item
  \faBook \hspace{0.005in} \textbf{DSW}: Daynes, Byron W., Glen Sussman,
  and Jonathan P. West. 2016. American Politics and the Environment. 2nd
  ed.~Albany, NY: State University of New York Press.

  \begin{itemize}
  
  \item
    Chapters posted on \href{https://lms.cofc.edu}{OAKS}.
  \end{itemize}
\item
  Apart from the book, additional required readings will be available on
  \href{https://lms.cofc.edu}{OAKS} for some weeks
\item
  You should should read in the order provided below and plan on reading
  about half of the material before Tuesday and the other half before
  Thursday each week. Additional guidance on the readings will be
  provided during the lectures.
\end{itemize}

\SetDate[04/01/2022]

\week \textbf{Introduction and Course Overview}

\emph{Readings}:

\begin{itemize}
\item
  \textbf{RP}: Chapter 1, \emph{Environmental Policy in Practice}, pgs.
  1-9
\item
  \textbf{DSW}: Chapter 1, \emph{The American Political Setting and the
  Environment}, pgs. 1-9
\end{itemize}

\week \textbf{Environmental Values and Value Conflict}

\emph{Readings}:

\begin{itemize}
\item
  \textbf{Nowlin}: Chapter 4, \emph{Value Systems and Environmental
  Policy}, on \href{https://lms.cofc.edu}{OAKS}
\item
  Kahan, Dan M., Ellen Peters, Maggie Wittlin, Paul Slovic, Lisa
  Larrimore Ouellette, Donald Braman, and Gregory Mandel. 2012. ``The
  Polarizing Impact of Science Literacy and Numeracy on Perceived
  Climate Change Risks.'' \emph{Nature Climate Change} 2(10): 732--35,
  on \href{https://lms.cofc.edu}{OAKS}
\end{itemize}

\week \textbf{Evolution of Environmental Policy in the United States}

\emph{Readings}:

\begin{itemize}
\item
  \textbf{RP}: Chapter 2, \emph{The Development and Context of American
  Environmental Policy}
\item
  Mohai, Paul, David Pellow, and J. Timmons Roberts. 2009.
  ``Environmental Justice.'' \emph{Annual Review of Environment and
  Resources} 34(1): 405--30, on \href{https://lms.cofc.edu}{OAKS}
\end{itemize}

\week \textbf{Environmental Policymaking}

\emph{Readings}:

\begin{itemize}

\item
  \textbf{RP}: Chapter 3, \emph{The Messy Process of Making
  Environmental Policy}
\end{itemize}

\vspace{0.10in} \emph{Assignments}:

\begin{itemize}

\item
  Environmental policy brief topic due Thursday Feb 3
\end{itemize}

\week \textbf{Unofficial Actors}

\emph{Readings}:

\begin{itemize}
\item
  \textbf{RP}: Chapter 5, \emph{Unofficial Actors in the Policy Process}
\item
  \textbf{DSW} Chapter 3, \emph{Public Opinion, Interest Groups, and the
  Environment}
\end{itemize}

\week \textbf{Official Actors: Congress}

\emph{Readings}:

\begin{itemize}
\item
  \textbf{RP}: Chapter 4, \emph{Official Actors in the Policy Process},
  pgs. 111-122
\item
  \textbf{DSW}: Chapter 4, \emph{Congress, the Legislative Process, and
  the Environment}
\end{itemize}

\week \textbf{Official Actors: The Executive}

\emph{Readings}:

\begin{itemize}

\item
  \textbf{RP}: Chapter 4, \emph{Official Actors in the Policy Process},
  pgs. 122-141
\end{itemize}

\vspace{0.10in}

\emph{Assignments}:

\begin{itemize}

\item
  Annotated bibliography due, Thursday Feb 24
\end{itemize}

\week \textbf{Official Actors: The Courts}

\emph{Readings}:

\begin{itemize}

\item
  \textbf{RP}: Chapter 4, \emph{Official Actors in the Policy Process},
  pgs. 141-147
\end{itemize}

\vspace{0.10in}

\emph{Assignments}:

\begin{itemize}

\item
  \textbf{MID-TERM EXAM: March 3}
\end{itemize}

\week \textbf{Spring Break}

\week \textbf{Federalism and Environmental Policy Design}

\emph{Readings}:

\begin{itemize}

\item
  \textbf{DSW}: Chapter 2, \emph{American Federalism and Environmental
  Politics}
\end{itemize}

\week \textbf{Environmental Regulation}

\emph{Readings}:

\begin{itemize}
\item
  \textbf{RP}: Chapter 6, \emph{Translating Vague Statutes into Rules
  and Regulations}
\item
  \textbf{RP}: Chapter 7, \emph{Implementing Environmental Policy and
  Regulations: Where the Rubber Meets the Road}
\end{itemize}

\week \textbf{Market-Based Environmental Policy}

\emph{Readings}:

\begin{itemize}

\item
  \textbf{Keohane and Olmstead}. 2016. ``Principles of Market-Based
  Environmental Policy'' from \emph{Markets and the Environment}, on
  \href{https://lms.cofc.edu}{OAKS}.
\end{itemize}

\vspace{0.10in}

\emph{Assignments}:

\begin{itemize}

\item
  Fact sheet due, Thursday March 31
\end{itemize}

\week \textbf{Pollution Control}

\emph{Readings}:

\begin{itemize}

\item
  \textbf{Andrews}: Chapter 12, \emph{The EPA: Nationalizing Pollution
  Control}, on \href{https://lms.cofc.edu}{OAKS}
\end{itemize}

\week \textbf{Public Lands}

\emph{Readings}:

\begin{itemize}

\item
  \textbf{Andrews}: Chapter 13, \emph{Public Lands and Wildlife
  Conservation}, on \href{https://lms.cofc.edu}{OAKS}
\end{itemize}

\week \textbf{Energy}

\emph{Readings}:

\begin{itemize}

\item
  \textbf{Andrews}: Chapter 15, \emph{Energy Policy and Climate Change},
  on \href{https://lms.cofc.edu}{OAKS}
\end{itemize}

\vspace{0.10in}

\emph{Assignments}:

\begin{itemize}

\item
  Policy brief due, Thursday April 21
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\noindent \textbf{FINAL EXAM DATE IS THURSDAY APRIL 28}
